\chapter{Search for compressed Higgsinos with soft lepton tracks}
\label{sec:search}

In this chapter, the search for compressed Higgsinos with soft lepton tracks is presented.
First, the model considered in this search is introduced and motivated, followed by a description of previous searches conducted for such a signature. The search strategy is then described in a general way to provide an overview of the analysis. Later, the data sets and simulated samples used are listed. The main description of the analysis begins with an exploration of the signal signature and base selection. This is followed by the definition and selection of objects, as well as the event selection and trigger used. Background sources are then identified, and the procedures used to estimate them are described in detail in the subsequent section. Data control plots are presented to compare simulations with the data in control regions. The search bins that constitute the signal regions are described, along with the optimization procedure employed to define them. Sources of systematic uncertainties are estimated for the background estimation methods, followed by validation studies for the background. Data quality aspects are also explored in this chapter. It concludes with the expected results based on the full Run 2 luminosity of 137\fbinv, as well as the observed results obtained from the partial unblinding of 10\% of the data collected by CMS at a center-of-mass energy of $\sqrt{s}=13\TeV$.


\input{search-introduction}
\input{previous-searches}
\input{search-strategy}
\input{simulated-samples}

\input{signal-signature}

%don't capitalise 
\input{object-selection}

\input{event-selection}

\input{trigger}

\input{background}

\input{data-control-plots}

\input{signal-regions}

\input{systematic-uncertainties}

\input{data-quality}

\input{results}



